Reproducible Research: A Tutorial on how to do the same thing more than once in R

### 2021-08-04 manuscript.Rmd
add abbrevation WORCS
remove "fail to guarantee" closes #168

    long: Preregistration as 

@@

@@

One would hope that sharing a dynamic document would allow individuals (including one's future self) to simply download and reproduce a given analysis.
However, while version control and dynamic document generation are becoming more common, this approach fails to guarantee reproducibility in many instances [@Peikert2019].
In practice, dependencies between project files (for example, the information what script uses which data file and what script needs to be run first) or on external software (such as system libraries or components of the programming language, such as other R packages) are frequently unmentioned or not exhaustively and unambiguously documented.

>>>>

    long: Preregistration as Code

@@

  - short: WORCS
    long: Workflow for Open Reproducible Code in Science

@@

One would hope that sharing a dynamic document would allow individuals (including one's future self) to simply download and reproduce a given analysis.
While version control and dynamic document generation are becoming more common, we have argued that two more components are required and that each component alone is unlikely to guarantee reproducibility [@Peikert2019; @vanlissa2020worcs].
In practice, dependencies between project files (for example, the information what script uses which data file and what script needs to be run first) or on external software (such as system libraries or components of the programming language, such as other R packages) are frequently unmentioned or not exhaustively and unambiguously documented.
